Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-29 paper/ms.tex
Add caption to histogram plot

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{Caption.}
\label{fig:Jz_hist}
\end{figure}

>>>>

\begin{figure}
\plotone{fig/schmactions_Jz_hist.pdf}
\caption{A histogram of the observed values in $J_z$ for the thick orbit
assuming a $z$ offset of $100\,\pc$. One can see that if the observed $z$
values have a bias (from e.g. an incorrectly computed midplane), then the
induced error distribution in $J_z$ is decidedly non-Gaussian. Therefore, any
sort of error propagation must take this into account.}
\label{fig:Jz_hist}
\end{figure}
